R Notebook

### 2017-03-31 doc/RMD/MLG-distribution.Rmd
update graphing

pop_graph <- crosses %>%
  group_by(MLG) %>% 
  summarize(Population = list(make_from_to(Population)), Size = sum(Count)) %>%
  unnest() %>%
  group_by(from, to) %>%
  summarize(weight = length(Size)) %>%
  ungroup()

gcross <- graph_from_data_frame(pop_graph, directed = FALSE)
traffic <- apply(gcross[], 1, sum)
# V(gcross)$weight <- table(pop(clonecorrect(dat, ~Region)))[V(gcross)]
colors <- viridis::magma(max(pop_graph$weight), end = 0.9)
set.seed(50)
gcross %>%
  plot(., vertex.size = table(pop(clonecorrect(dat, ~Region)))[names(V(gcross))],
       edge.width = E(.)$weight, 
       layout = layout_in_circle(.),
       edge.color = colors[E(.)$weight])

@@

>>>>

pg <- 
  crosses %>%
  group_by(MLG) %>% 
  summarize(Population = list(make_from_to(Population)), Size = length(Count))

pop_graph <- pg %>%  unnest() %>%
  group_by(from, to) %>%
  mutate(weight = length(Size)) %>%
  ungroup() %>%
  select(from, to, weight, everything())

unchoose <- function(x) ceiling(sqrt(x * 2))

gcross           <- graph_from_data_frame(pop_graph, directed = FALSE)
E(gcross)$name   <- as.character(pop_graph$MLG)
E(gcross)$weight <- unchoose(table(E(gcross)$name)[E(gcross)$name])
colors <- viridis::magma(max(E(gcross)$weight) - 1, end = 0.8)
set.seed(50)
gcross %>%
  plot(., vertex.size = table(pop(clonecorrect(dat, ~Region)))[names(V(gcross))],
       edge.width = E(.)$weight - 1,
       layout = layout_as_star(., center = "MI"),
       # layout = layout_in_circle(.),
       edge.color = colors[E(.)$weight - 1])

@@

```{r}

pops <- crosses %>%
  group_by(Population) %>%
  summarize(MLG = list(as.character(MLG))) %>%
  group_by(Population) %>%
  mutate(interactions = list(pg$Population[pg$MLG %in% unlist(MLG)] %>% setNames(unlist(MLG)) %>% bind_rows(.id = "MLG") %>% distinct)) %>%
  mutate(graph = map(interactions, ~select(.x, from, to, MLG) %>% graph_from_data_frame(directed = FALSE)))
psize <- table(pop(clonecorrect(dat, ~Region)))
par(mfrow = c(3, 4))

apply(pops, 1, function(i){
    plot(i$graph, 
         layout = layout_as_star(i$graph, center = i$Population), 
         main = i$Population, 
         vertex.size = psize[names(V(i$graph))])
  })
par(mfrow = c(1, 1))
do.call("union", pops$graph) %>% 
  plot(., vertex.size = psize[names(V(.))],
       layout = layout_as_star(., center = "MI"))
```
